Repeatability Test

### 2017-07-16 pt_characterization/rep_check/1024_run.tex
Refactoring files for Characterizing paper

\section{Histograms on Consecutive INC1024 Runs~\label{sec:s9_1024_runs}} 
This section exhibits histograms on (three) consecutive runs of INC1024 via SEDONA. 
The detailed description of the base data is from Table~\ref{tab:exp_notes2}.

>>>>

\section{Histograms on Consecutive INC1024 Runs~\label{sec:s9_1024_runs}} 
This section exhibits histograms on (three) consecutive runs of INC1024. 
The detailed description of the base data is from Table~\ref{tab:exp_notes2}.

### 2017-07-16 pt_characterization/rep_check/paper.tex
Change the name of the protocol
DRAFT for May 31
Draft being ready for July 10
Refactoring files for Characterizing paper

\section{Description}
This document presents two sets of histograms based on the two runs 
of a program under test, called {\em INC}, with a set of increasing task lengths 
from 1 second to 4096 seconds.
We would like to see if both of the sets have the same shape for the same task length.
If so then, we can say that run repeatability is satisfied in our experiment setting. 
%In this study the used protocol is equivalent to SEDONA~\cite{Sedona}, 
%eliminating samples involving infrequent, long-running daemons, which is the first step of EMPv5.
In this study the used protocol eliminates samples involving infrequent, long-running daemons, 
which is the first step of EMPv5.

In the protocol, we use taskstats C struct to get measures of a captured process. 
The taskstat's data is delivered via a netlink socket from the kernel space. 
The receive buffer for the socket is not robust for many observed processes~\cite{Metrology}. 
Fortunately, there is an average of 95 processes per iteration of a run, 
which turns out to be fine with the struct. 
For a much more number of processes, 
the use of  {\tt /proc/}[pid]{\tt{/stat}} is preferred, 
as (i) there are equivalent measures available in the {\tt /proc} filesystem, 
and (ii) there's little constraint on the use as opposed to taskstats.

Now we show histograms of elapsed time (ET) and process time (PT) of INC via the SEDONA protocol.

@@

@@

\bibliographystyle{abbrv}
\newcommand{\etalchar}[1]{$^{#1}$}
\begin{thebibliography}{99}
\vspace{0.1em}
\bibitem
%{Avnur:2000:ECA:342009.335420}
%{Sedona}
%Young-Kyoon Suh, ``SEDONA: A Novel Protocol for Identifying Infrequent, Long-running Daemons on a Linux System'', in {\em IEICE Transactions on Information Systems}, Vol. 100D, No. 9, pp.~??--??, 2017.
\vspace{0.1em}
\bibitem
%{Avnur:2000:ECA:342009.335420}
{Metrology}
Sabah Currim,Richard T. Snodgrass, Young-Kyoon Suh, and Rui Zhang, ``DBMS Metrology: Measuring Query Time'', in {\em ACM Transactions on Database Systems}, 42(1):3:1--42(+8), 2017.
\end{thebibliography}

>>>>

\section{Description}
This document characterizes execution times 
measured on a simple program in pure-computation mode, called {\em INC}, 
with increasing task lengths (up to 16,384 seconds from 1 second). 
For the characterization, we present various histograms of INC throughout this document.
The main goal of examining these histograms is to make sure if 
two (or more) histograms of INC with the same task length 
have the same shape or not. If that's the case, then we can say that such an INC run is so called {\em repeatable}; 
in other words, {\em repeatability} is satisfied in our experimental settings. 
Another goal is to uncover and explicate several interesting structures behind the histograms. 
The third goal is to build a statistical distribution (or model) fitting in the histograms, so that later we 
are capable of predicting a concrete execution time via 
the model on an arbitrary algorithm with a given input on a real execution environment.

In our experiments, we used EMPv5~\cite{EMP}. 
(That said, the second step of EMPv5 was on purpose omitted, just to obtain better histograms by retaining more samples.) 
In the protocol, we use taskstats C struct to get measures of a captured process. 
The taskstat's data is delivered via a netlink socket from the kernel space. 
The receive buffer for the socket is not robust for many observed processes~\cite{Metrology}. 
Fortunately, there is an average of 95 processes per iteration of a run, 
which turns out to be fine with the struct. 
For a much more number of processes, 
the use of  {\tt /proc/}[pid]{\tt{/stat}} is preferred, 
as (i) there are equivalent measures available in the {\tt /proc} filesystem, 
and (ii) there's little constraint on the use as opposed to taskstats.

Now we show histograms of elapsed time (ET) and process time (PT) of INC via the EMPv5 protocol.

@@

%\pagebreak
%\newpage
%
%\input{further.tex}

@@

\bibliographystyle{abbrv}
\newcommand{\etalchar}[1]{$^{#1}$}
\begin{thebibliography}{99}
\vspace{0.1em}
%\bibitem
%{Avnur:2000:ECA:342009.335420}
%{Sedona}
%Young-Kyoon Suh, ``SEDONA: A Novel Protocol for Identifying Infrequent, Long-running Daemons on a Linux System'', in {\em IEICE Transactions on Information Systems}, Vol. 100D, No. 9, pp.~??--??, 2017.
%\vspace{0.1em}
\bibitem
%{Avnur:2000:ECA:342009.335420}
{EMP}
Young-Kyoon Suh, Richard T. Snodgrass, John Kececioglu, Peter J. Downey, Rob S. Maier, and Cheng Yi, ``EMP: Execution Time Measurement Protocol for Compute-Bound Programs'', in {\em Software: Practice and Experience}, 47(4):559--597, 2017.
\bibitem
%{Avnur:2000:ECA:342009.335420}
{Metrology}
Sabah Currim,Richard T. Snodgrass, Young-Kyoon Suh, and Rui Zhang, ``DBMS Metrology: Measuring Query Time'', in {\em ACM Transactions on Database Systems}, 42(1):3:1--42(+8), 2017.
\end{thebibliography}

### 2017-07-16 pt_characterization/rep_check/res1.tex
Refactoring files for Characterizing paper

\section{Histograms on the First Run~\label{sec:sodb9_r1_hist}} 
This section exhibits histograms on the first run of 
INC with its task length increasing from 1 second to 4096 seconds, via EMPv5. 
The detailed description of the base data is from Table~\ref{tab:exp_notes1}.

>>>>

\section{Histograms on the First Run~\label{sec:sodb9_r1_hist}} 
This section exhibits histograms on the first run of 
INC with its task length increasing from 1 second to 4096 seconds. 
The detailed description of the base data is from Table~\ref{tab:exp_notes1}.

### 2017-07-16 pt_characterization/rep_check/temp/further.tex
Refactoring files for Characterizing paper

\section{A Characterization Study on the First Run~\label{sec:sodb9_r3_hist}} 
This section further discusses the first run of 
INC with its task length increasing from 1 second to 4096 seconds via EMPv5 with no Step 2. 
The detailed description of the base data is from Table~\ref{tab:exp_notes3}.

%\begin{table}[h]
%\begin{center}
%\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
%Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
%{\tt sodb9} &  INC1$\sim$INC64 & 1000 samples, each & 2017-03-13 $\sim$ 2017-03-14 & %Figs.~\ref{fig:s9_r2_et_hist1},~\ref{fig:s9_r2_et_hist2},~\ref{fig:s9_r2_pt_hist1}, and~\ref{fig:s9_r2_pt_hist2}\\ \hline
%{\tt sodb9} &  INC512$\sim$INC1024 & 300 samples, each & 2017-03-17 $\sim$ 2017-03-21 & 
%%Figs.~\ref{fig:s9_r2_et_hist3} and~\ref{fig:s9_r2_pt_hist3}\\ \hline
%{\tt sodb10} & INC2048 & 300 samples & 2017-03-13 $\sim$ 2017-03-20 & 
%%Figs.~\ref{fig:inc2048_r2_et_hist_v5} and~\ref{fig:inc2048_r2_hist_v5}\\ \hline
%{\tt sodb12} & INC4096 & 300 samples & 2017-03-02 $\sim$ 2017-03-17 & 
%%Figs.~\ref{fig:inc4096_r2_et_hist_v5} and~\ref{fig:inc4096_r2_hist_v5}\\ \hline
%{\tt sodb10} & INC8192& 261 samples & 2017-04-27 $\sim$ 2017-05-21 & 
%%Figs.~\ref{fig:inc8192_r2_et_hist_v5} and~\ref{fig:inc8192_r2_hist_v5}\\ \hline
%{\tt sodb12} & INC16384& 130 samples & 2017-04-27 $\sim$ 2017-05-21 & 
%%Figs.~\ref{fig:inc16384_r2_et_hist_v5} and~\ref{fig:inc16384_r2_hist_v5}\\ \hline
%\end{tabular}
%\end{center}
%\vspace{-.2in}
%\caption{Notes on experiment runs used for histograms\label{tab:exp_notes3}}
%\end{table}
%
%INC8192/INC16384 unfortunately stopped in the middle of their runs due to a frozen vnc problem. So couldn't finish 300 samples.
%
%\pagebreak

@@

\subsection{ET}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1]{
		\includegraphics[scale=0.43]{u_s_time/1_sec_et_hist.eps}
		\label{fig:inc1_r3_et_hist_v5}
	}
	\subfigure[ET frequency on INC2]{
		\includegraphics[scale=0.43]{u_s_time/2_sec_et_hist.eps}
		\label{fig:inc2_r3_et_hist_v5}
	}
	\subfigure[ET frequency on INC4]{
		\includegraphics[scale=0.43]{u_s_time/4_sec_et_hist.eps}
		\label{fig:inc4_r3_et_hist_v5}
	}
	\subfigure[ET frequency on INC8]{
		\includegraphics[scale=0.43]{u_s_time/8_sec_et_hist.eps}
		\label{fig:inc8_r3_et_hist_v5}
	}
	\caption{ET Histograms of INC1 ... INC8~\label{fig:s9_r3_et_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC16]{
		\includegraphics[scale=0.43]{u_s_time/16_sec_et_hist.eps}
		\label{fig:inc16_r3_et_hist_v5}
	}
	\subfigure[ET frequency on INC32]{
		\includegraphics[scale=0.43]{u_s_time/32_sec_et_hist.eps}
		\label{fig:inc32_r3_et_hist_v5}
	}
	\subfigure[ET frequency on INC64]{
		\includegraphics[scale=0.43]{u_s_time/64_sec_et_hist.eps}
		\label{fig:inc64_r3_et_hist_v5}
	}
	\caption{ET Histograms of INC16 ... INC64~\label{fig:s9_r3_et_hist2}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC128]{
		\includegraphics[scale=0.43]{u_s_time/128_sec_et_hist.eps}
		\label{fig:inc128_r3_et_hist_v5}
	}
	\subfigure[ET frequency on INC256]{
		\includegraphics[scale=0.43]{u_s_time/256_sec_et_hist.eps}
		\label{fig:inc256_r3_et_hist_v5}
	}
	\subfigure[ET frequency on INC512]{
		\includegraphics[scale=0.43]{u_s_time/512_sec_et_hist.eps}
		\label{fig:inc512_r3_et_hist_v5}
	}
	\subfigure[ET frequency on INC1024]{
		\includegraphics[scale=0.43]{u_s_time/1024_sec_et_hist.eps}
		\label{fig:inc1024_r3_et_hist_v5}
	}
	\caption{ET Histograms of INC128 ... INC1024~\label{fig:s9_r3_et_hist3}}
\end{figure}

%\begin{figure}[hp!]
%	\centering
%	\subfigure[ET frequency on INC2048]{
%		\includegraphics[scale=0.43]{u_s_time/2048_sec_et_hist.eps}
%		\label{fig:inc2048_r3_et_hist_v5}
%	}
%	\subfigure[ET frequency on INC4096]{
%		\includegraphics[scale=0.43]{u_s_time/4096_sec_et_hist.eps}
%		\label{fig:inc4096_r3_et_hist_v5}
%	}
%	\caption{ET Histograms of INC2048 ... INC4096~\label{fig:s9_r3_et_hist4}}
%\end{figure}

\vspace\fill
\clearpage

\subsection{PT}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1]{
		\includegraphics[scale=0.43]{u_s_time/1_sec_pt_hist.eps}
		\label{fig:inc1_r3_hist_v5}
	}
	\subfigure[PT frequency on INC2]{
		\includegraphics[scale=0.43]{u_s_time/2_sec_pt_hist.eps}
		\label{fig:inc2_r3_hist_v5}
	}
	\subfigure[PT frequency on INC4]{
		\includegraphics[scale=0.43]{u_s_time/4_sec_pt_hist.eps}
		\label{fig:inc4_r3_hist_v5}
	}
	\subfigure[PT frequency on INC8]{
		\includegraphics[scale=0.43]{u_s_time/8_sec_pt_hist.eps}
		\label{fig:inc8_r3_hist_v5}
	}
	\caption{PT Histograms of INC1 ... INC8~\label{fig:s9_r3_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{u_s_time/16_sec_pt_hist.eps}
		\label{fig:inc16_r3_hist_v5}
	}
	\subfigure[PT frequency on INC32]{
		\includegraphics[scale=0.43]{u_s_time/32_sec_pt_hist.eps}
		\label{fig:inc32_r3_hist_v5}
	}
	\subfigure[PT frequency on INC64]{
		\includegraphics[scale=0.43]{u_s_time/64_sec_pt_hist.eps}
		\label{fig:inc64_r3_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64\label{fig:s9_r3_pt_hist2}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC128]{
		\includegraphics[scale=0.43]{u_s_time/128_sec_pt_hist.eps}
		\label{fig:inc128_r3_hist_v5}
	}
	\subfigure[PT frequency on INC256]{
		\includegraphics[scale=0.43]{u_s_time/256_sec_pt_hist.eps}
		\label{fig:inc256_r3_hist_v5}
	}
	\subfigure[PT frequency on INC512]{
		\includegraphics[scale=0.43]{u_s_time/512_sec_pt_hist.eps}
		\label{fig:inc512_r3_hist_v5}
	}
	\subfigure[PT frequency on INC1024]{
		\includegraphics[scale=0.43]{u_s_time/1024_sec_pt_hist.eps}
		\label{fig:inc1024_r3_hist_v5}
	}
	\caption{PT Histograms of INC256 ... INC1024~\label{fig:s9_r3_pt_hist3}}
\end{figure}

%\begin{figure}[t]
%	\centering
%	\subfigure[PT frequency on INC2048]{
%		\includegraphics[scale=0.43]{u_s_time/2048_sec_pt_hist.eps}
%		\label{fig:inc2048_r3_hist_v5}
%	}
%	\subfigure[PT frequency on INC4096]{
%		\includegraphics[scale=0.43]{u_s_time/4096_sec_pt_hist.eps}
%		\label{fig:inc4096_r3_hist_v5}
%	}
%%	\subfigure[PT frequency on INC8192]{
%%		\includegraphics[scale=0.43]{u_s_time/8192_sec_pt_hist.eps}
%%		\label{fig:inc8192_r3_hist_v5}
%%	}
%%	\subfigure[PT frequency on INC16384]{
%%		\includegraphics[scale=0.43]{u_s_time/16384_sec_pt_hist.eps}
%%		\label{fig:inc16384_r3_hist_v5}
%%	}
%	\caption{PT Histograms of INC2048 ... INC16384~\label{fig:s9_r3_pt_hist4}}
%\end{figure}

\clearpage

>>>>

\section{A Characterization Study on the First Run~\label{sec:sodb9_r3_hist}} 
This section further discusses the first run of 
INC with its task length increasing from 1 second to 4096 seconds via EMPv5 with no Step 2. 
The detailed description of the base data is from Table~\ref{tab:exp_notes1}.

@@
